Water, High-Altitude Condensates, and Methane Depletion in the Atmosphere of the Warm Neptune WASP-107\lowercase{b}

### 2017-08-13 ms.tex
ctoo

\subsection{Retrieval}
\label{sec:retrieval}
We also inferred the composition of the atmosphere directly from the transmission spectrum using the CHIMERA chemically-consistent retrieval tool described in \cite{kreidberg15b}.   Briefly, CHIMERA solves the transmission geometry problem using the equations in \cite{brown01, tinetti12}.  We parameterize atmospheric composition with metallicity and carbon-to-oxygen ratio (C/O) under the assumption of thermochemical equilibrium using the NASA CEA routine \citep{gordon96} to compute the molecular abundances for H$_2$, He, H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, H$_2$S, Na, K, HCN, C$_2$H$_2$, TiO, VO, and FeH.    We updated the transmission model to use correlated-K opacities \citep{lacis91, molliere15, amundsen16} for the aforementioned gases generated from the pre-tabulated line-by-line cross section database described in \cite{freedman14}. The transmission forward model is coupled with the powerful PyMultiNest tool \citep{buchner16} to solve the parameter estimation and model selection problems.

The nominal model set-up requires a temperature-pressure profile (parameterized via the \citealt{guillot10} relations), the atmospheric metallicity and carbon-to-oxygen ratio for molecular composition determination, disquilibrium properties crudely parameterized with nitrogen species and carbon species quench pressures \citep{morley17}, and aerosol properties.  We experiment with three atmospheric scenarios within this setup: scenarios with and without methane, and with/without patchy cloud cover (as described and implemented in \citealt{line16}.  In all three scenarios we fix the T-P profile ``shape" but scale the irradiation temperature, to allow for the unknown albedo and heat transport efficiency.  T-P profile shape information is not readily retrievable, nor does it strongly influence information derived from WFC3 transmission spectra \citep[e.g.][]{kreidberg15b}.  Aerosols are parameterized with a ``gray cloud top pressure" with the option for cloud patchiness. %We do not consider ``sloped hazes" at this time as they are unlikely to influence the results.
%We also switch off the quench pressure parameters as they are unlikely to strongly influence the equilibrium abundance profiles of the spectrally prominent, nearly constant-with-altitude abundance, species like CH$_4$, H$_2$O, and NH$_3$ over this temperature range \citep[e.g.][]{line11, moses13}.

>>>>

\subsection{Retrieval}
\label{sec:retrieval}
We also inferred the composition of the atmosphere directly from the transmission spectrum using the CHIMERA chemically-consistent retrieval tool described in \cite{kreidberg15b}.   Briefly, CHIMERA solves the transmission geometry problem using the equations in \cite{brown01, tinetti12}.  We parameterize atmospheric composition with metallicity and carbon-to-oxygen ratio (C/O) under the assumption of thermochemical equilibrium using the NASA CEA routine \citep{gordon96} to compute the molecular abundances for H$_2$, He, H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, H$_2$S, Na, K, HCN, C$_2$H$_2$, TiO, VO, and FeH.    We updated the transmission model to use correlated-K opacities \citep{lacis91, molliere15, amundsen16} for the aforementioned gases from the pre-tabulated line-by-line cross section database described in \cite{freedman14}. The transmission forward model is coupled with the powerful PyMultiNest tool \citep{buchner16} to solve the parameter estimation and model selection problems.

The nominal model set-up requires a temperature-pressure profile (parameterized via the \citealt{guillot10} relations), the atmospheric metallicity and carbon-to-oxygen ratio for molecular composition determination, disequilibrium properties parameterized with nitrogen and carbon species quench pressures \citep{morley17}, and aerosol properties.  We fix the T-P profile morphology but scale the irradiation temperature to allow for the unknown albedo and heat transport efficiency.  Aerosols are parameterized with a gray cloud top pressure with the option for cloud patchiness (as described by \citealt{line16}).

Our nominal model included a gray cloud, prior

We experiment with several scenarios within this framework, including models with/without clouds, models with/without quenching, including methane opacity, and a uniform prior in atmospheric metallicity from (FIXME to $30\times$ solar based on the interior structure modeling). We also performed a ``free" retrieval that allowed the abundances of CH$_4$, H$_2$O and NH$_3$ to vary freely.

We find strong evidence for water absorption (FIXME sigma) and clouds (FIXME sigma).

%We do not consider ``sloped hazes" at this time as they are unlikely to influence the results.
%We also switch off the quench pressure parameters as they are unlikely to strongly influence the equilibrium abundance profiles of the spectrally prominent, nearly constant-with-altitude abundance, species like CH$_4$, H$_2$O, and NH$_3$ over this temperature range \citep[e.g.][]{line11, moses13}.
